A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-23 documents/plm.tex
predicted pixels

Once we have obtained the $a_{mnm'}$ parameters corresponding to data point $I_{mn}$ by minimizing the training objective $\chi^2_{mn}$.

>>>>

Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
In addition to the predicted pixel value $I^{\ast}_{mnn}$,
  we can also construct a \emph{residual} $\Delta_{mn}$ (data minus prediction),
  defined by
\begin{eqnarray}
\Delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
\quad .
\end{eqnarray}
